---
title: "TUD FOR WEEKDAYS"
author: "Kakau with minor amendments from Ben :-)"
date: 'Last run at: `r Sys.time()`'
output:
  bookdown::html_document2:
    fig_caption: yes
    code_folding: hide
    number_sections: yes
    toc: yes
    toc_depth: 2
    toc_float: TRUE
---

```{r setup}
# packages ----
library(plyr)
library(stringr)
library(tidyverse)
library(tidyr)
library(lubridate)
library(kableExtra)
library(dplyr)
library(scales)
library(ggplot2)

# parameters ----
dPath <- "/Volumes/hum-csafe/Research Projects/FoliakiPhD/tudData/" # edit for your set up
dataF <- path.expand(paste0(dPath, "TUD Weekdays.csv"))
  
```

# Time Use Diary


Importing Weekends dataframe

The dataframe is a wide format. I had to clean the data by correcting typo and translating some of the data into english. So the file is not as original as it is when export from qualtrics. 

```{r loadData}

# read in my dataframe
weekdays <- read.csv(dataF, na.strings=c(""), check.names = FALSE, header = TRUE, as.is=TRUE)

head(weekdays)



```


Converting the wide dataframe to long dataframe for easier analysis

Ive noticed that the time is in a character format rather than date. i need to change it to date

> see below

```{r makeLong}

longweekdays <- weekdays %>%
  gather(Time, Activity, 4:51)

head(longweekdays)

```

Sorting the TUD dataframe, Firstly, as you can see previously some respondents do not have a secondary activity (i.e NA). Secondly, the data is sorted by time. I think it would be easier to sorted by Household ID. So here i am sorting the data based on ID number

```{r sortByID}
# sorting my dataframe in accending order based on the Household ID
weekdayOrder <- order(longweekdays$`Household ID`)
head(weekdayOrder)

# Applying the sorting order into my "longweekdends" dataframe and call it sortweekends
sortweekdays <- longweekdays[weekdayOrder,]
head(sortweekdays)

names(sortweekdays)
```


Here i am seprating the activity columm into a primary activity and a secondary activity

The issue im facing with is the date. It in character and alsoit picked up the current date (2020) rather than the date from the TUD.

> BA: I can't see a date variable. How would R know which date the diary was completed on?

Im trying to sort the date but it comes back N/A

> see below

```{r rearrangeActs}
# Since both the first and second activiies are in one column, i need to separate them into two columns

#call the number of row in my dataframe for the maximum row for my sequence function
nrow(sortweekdays)

#create a new dataframe "newdata" for the primary activity only (all odd rows)
newdata <- sortweekdays[seq(1,8351,2),]
head(newdata)

#create a new datagame "newdata1" for the secondary activity (oall even rows)
newdata1 <- sortweekdays[seq(2,8352,2),]
head(newdata1)

#since i have separated my two acitvities, i need to merge them into one dataframe
newdata$Activity2 <- newdata1$Activity

kableExtra::kable(head(newdata), caption = "Test merged long form data") %>%
  kable_styling()


```

> BA: fix the time variable so it looks like and acts like HH:MM

```{r fixTime}
#newdata$rawTime <- hms::parse_hm(newdata$Time) # this will only be right for AM
#newdata$AM_PM <- stringr::word(newdata$Time, 2) # get the second word of 'Time' which will be AM or PM

# better solution
# https://stackoverflow.com/questions/7883806/parse-timestamp-with-a-m-p-m
# this will make it today's date and the current time zone by default
newdata$rawTime <- as.POSIXct(newdata$Time, format="%l:%M %p")

# Lesson #1: always enter times as 24 hour clock: HH:MM !!

# Now use that to add 12 hours to rawTime whenit is actually PM
# newdata$fixedTime <- ifelse(newdata$AM_PM =="PM", # if PM
#                             newdata$rawTime + (12 * 60 * 60), #  add 12 hours
#                             newdata$rawTime # otherwise don't
#                             ) 
newdata$fixedHMS <- hms::as_hms(newdata$rawTime) # make sure it is in H:M:S format

t <- table(newdata$Time, newdata$rawTime)
kableExtra::kable(t, caption = "Test time coding") %>%
  kable_styling()
```

# Weekdays TUD

Here i am trying to seprate the data into days so i can analyse the activities.

```{r createWeekdayDataFrames}

#filter newdata dataframe by date using the dplyr

#creating a new dataframe "Monday"
monday <- dplyr::filter(newdata, Day == "Monday")
head(monday)

#creating a new dataframe "Tuesday"
tuesday <- dplyr::filter(newdata, Day == "Tuesday")
head(tuesday)

#creating a new dataframe "Wednesday"
wednesday <- dplyr::filter(newdata, Day == "Wednesday")
head(wednesday)

#creating a new dataframe "Thursday"
thursday <- dplyr::filter(newdata, Day == "Thursday")
head(thursday)

#creating a new dataframe "Friday"
friday <- dplyr::filter(newdata, Day == "Friday")
head(friday)


```


# Monday

So im trying to sort out the coding for Monday so i can copy it for the rest of the weekdays. I've did a frequency and proportion of activities for Monday.

```{r testMonday}



#frequency of Activities
freqA <- table(monday$Activity, exclude=NULL)
freqA
dim(freqA)

#proportion of Activities
propA <- prop.table(freqA)*100
propA <- round(propA, digits=2)
propA

dim(propA)

#creating table with binding
tableMon <- cbind(freqA, propA)
tableMon <- cbind(Gender = rownames(tableMon), tableMon)
rownames(tableMon) <- NULL
tableMon

#rename column names
colnames(tableMon)[colnames(tableMon) == "freqA"] <- "Frequency"
colnames(tableMon)[colnames(tableMon) == "propA"] <- "Proportion (%)"
tableMon

#using kable extra to create better table format
tableMonday <- kable(tableMon)%>%
  kable_styling(bootstrap_options = "striped", full_width = F)

tableMonday

```


## Monday TUD
Im trying to see the count for all the activities in the TUD

```{r mondayGroupActs}
groupbymonAct <- monday %>%
  dplyr::group_by(Activity) %>%
  dplyr::summarize(count = n())
groupbymonAct

```

Im am trying to remove sleeping, rest, going to work from the data so that i can only focus on the rest of the acitivities.

The issue i am facing as the time is not sorted in accending order. Can you help with the coding

> yep - see what I did :-)

```{r mondayFilter}
tableAll <- monday %>%
  #select(Time, Activity) %>% 
  select(fixedHMS, Activity) %>% # use the new time variable
  filter(Activity != "Sleeping") %>%
  filter(Activity != "Rest") %>%
  filter(Activity != "Work") %>%
  #group_by(Time) %>% 
  group_by(fixedHMS) %>% 
  tally

kableExtra::kable(tableAll, caption = "Monday test (no sleep/rest/work)") %>%
  kable_styling()

# plot
ggplot2::ggplot(tableAll, aes(x = fixedHMS, y = n)) +
  geom_col()
```

## Monday Cooking

Here im am trying to look at anything related to preparing and eating a meal. 

```{r mondayCook}
# creating dataframe for all cooking

tableCooking <- monday %>%
  select(fixedHMS, Activity) %>% 
  filter(Activity != "Sleeping") %>%
  filter(Activity != "Rest") %>%
  filter(Activity != "Work") %>%
  filter(Activity %in% c("Cooking", 
                         "Cooking (business)", 
                         "Cooking (baby)",
                         "Cooking (lunch)", 
                         "Food prep (business)", 
                         "Lunch", 
                         "Breakfast", 
                         "Dinner", 
                         "Light meal/snack")) %>% 
  group_by(fixedHMS) %>% 
  tally
  
  
tableCooking

b <- ggplot(tableCooking, aes(x = fixedHMS, y = n)) + geom_bar(stat = "identity", position = "stack", color="blue", fill="blue") +
  ggtitle("(b) Cooking") +
  xlab("Time ") +
  ylab("n") + theme(plot.title = element_text(color="Black", size=11, face="bold.italic", hjust=0.5,lineheight=0.8),
        axis.title.x = element_text(color="black", size=10, face="bold"),
        axis.title.y = element_text(color="black", size=10, face="bold"),
        panel.background=element_rect(fill = "white"),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(), 
        axis.line = element_line(colour = "black", size = 1) + 
        scale_x_date(labels = date_format("%I:%M %p"))
)

b

```

## Monday Tidy up

similar to the above but for tidy up/cleaning up
```{r mondayTidyUp}
# creating dataframe for all cleaning up

tableTidyup <- monday %>%
  select(fixedHMS, Activity) %>% 
  filter(Activity != "Sleeping") %>% 
  filter(Activity != "Rest") %>%
  filter(Activity != "Work") %>%
  filter(Activity %in% c("Tidy up", 
                         "Laundry", 
                         "Showering", 
                         "Showering (kids)", 
                         "Gardening", 
                         "Getting dressed", 
                         "Getting dressed (kids)",
                         "Prepare kids bag for school",
                         "Turning off applicances/Lights", 
                         "Turning on appliances/lights", 
                         "Ironing", 
                         "Feeding animals")) %>% 
  group_by(fixedHMS) %>% 
  tally
  
  
tableTidyup

c <- ggplot(tableTidyup, aes(x = fixedHMS, y = n)) + geom_bar(stat = "identity", position = "stack", color="red", fill="red") +
  ggtitle("(c) Tidy up") +
  xlab("Time ") +
  ylab("n") + theme(plot.title = element_text(color="Black", size=11, face="bold.italic", hjust=0.5,lineheight=0.8),
        axis.title.x = element_text(color="black", size=10, face="bold"),
        axis.title.y = element_text(color="black", size=10, face="bold"),
        panel.background=element_rect(fill = "white"),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(), 
        axis.line = element_line(colour = "black", size = 1) + 
        scale_x_date(labels = date_format("%I:%M %p"))
)

c

```


## Monday Leisure
  similar to the above but for leisure
```{r momdayLeisure}
# creating dataframe for all leisure

tableleisure <- monday %>%
  select(fixedHMS, Activity) %>% 
  filter(Activity != "Sleeping") %>% 
  filter(Activity != "Rest") %>% 
  filter(Activity != "Work") %>%
  filter(Activity %in% c("Babysitting", 
                         "Charging mobile devices", 
                         "Family devotion",
                         "Exercise (Jog, walk)",
                         "Family time (chatting, games etc)",
                         "Homework (kids)",
                         "Kids bedtime",
                         "Listen to music/radio",
                         "Mobile devices (movies)",
                         "Mobile devices (games)",
                         "Mobile devices (work)",
                         "Mobile devices (browsing, social media)",
                         "Scripture study",
                         "Studying", 
                         "Reading",
                         "Watching movies (TV)")) %>% 
  group_by(fixedHMS) %>% 
  tally
  
  
tableleisure

d <- ggplot(tableleisure, aes(x = fixedHMS, y = n)) + geom_bar(stat = "identity", position = "stack", color="violet", fill="violet") +
  ggtitle("(d) Leisure") +
  xlab("Time ") +
  ylab("n") + theme(plot.title = element_text(color="Black", size=11, face="bold.italic", hjust=0.5,lineheight=0.8),
        axis.title.x = element_text(color="black", size=10, face="bold"),
        axis.title.y = element_text(color="black", size=10, face="bold"),
        panel.background=element_rect(fill = "white"),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(), 
        axis.line = element_line(colour = "black", size = 1) + 
        scale_x_date(labels = date_format("%I:%M %p"))
)

d
```

## Monday Away
similar to the above but for away from home
```{r mondayAway}
# creating dataframe for Away from Home

tableAway <- monday %>%
  select(fixedHMS, Activity) %>% 
  filter(Activity != "Sleeping") %>% 
  filter(Activity != "Rest") %>% 
  filter(Activity %in% c("Farm", 
                         "Relatives", 
                         "Work", 
                         "Kava", 
                         "Church", 
                         "Church (social activities)", 
                         "Church (choir practice)", 
                         "Exercise (Jog, walk)", 
                         "Gym",
                         "Sports",
                         "School", 
                         "Going out"))%>% 
  group_by(fixedHMS) %>% 
  tally
  
  
tableAway

e <- ggplot(tableAway, aes(x = fixedHMS, y = n)) + geom_bar(stat = "identity", position = "stack", color="orange", fill="orange") +
  ggtitle("(e) Away") +
  xlab("Time ") +
  ylab("n") + theme(plot.title = element_text(color="Black", size=11, face="bold.italic", hjust=0.5,lineheight=0.8),
        axis.title.x = element_text(color="black", size=10, face="bold"),
        axis.title.y = element_text(color="black", size=10, face="bold"),
        panel.background=element_rect(fill = "white"),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(), 
        axis.line = element_line(colour = "black", size = 1) + 
        scale_x_date(labels = date_format("%I:%M %p"))
)

e
```

## Monday Transport
similar to the above but for transportation

> BA: table breaks for some reason?

```{r mondayTransport}
# creating dataframe for transportation

tableTransport <- monday %>%
  select(fixedHMS, Activity) %>% 
  filter(Activity != "Sleeping") %>%
  filter(Activity != "Rest") %>%
  filter(Activity != "Work") %>%
  filter(Activity %in% c("Driving (church)", 
                         "Driving (drop kids)", 
                         "Driving (drop relatives)",
                         "Driving (farm)", 
                         "Driving (free time)", 
                         "Driving (gym)", 
                         "Driving (home)", 
                         "Driving (Kava)", 
                         "Driving (order delivery)", 
                         "Driving (pick up kids)", 
                         "Driving (visiting relatives)", 
                         "Driving (work)", 
                         "Public transport (home)", 
                         "Public transport (work)", 
                         "Public transport (school)", 
                         "Walking (home)",  
                         "Walking (work)", 
                         "Walking (Kava)")) %>% 
  group_by(fixedHMS) %>% 
  tally
  
  
tableTransport

#ploting Bar graph

f <- ggplot(tableTransport, aes(x = fixedHMS, y = n)) + geom_bar(stat = "identity", position = "stack", color="purple", fill="purple") +
  ggtitle("(e) Travelling") +
  xlab("Time ") +
  ylab("n") + theme(plot.title = element_text(color="Black", size=11, face="bold.italic", hjust=0.5,lineheight=0.8),
        axis.title.x = element_text(color="black", size=10, face="bold"),
        axis.title.y = element_text(color="black", size=10, face="bold"),
        panel.background=element_rect(fill = "white"),
        panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(), 
        axis.line = element_line(colour = "black", size = 1) + 
        scale_x_date(labels = date_format("%I:%M %p"))
)

f

```

## Monday Multiple plots

I wanted to put all the graphs in one page

```{r gridTheGraphs}
#graphs in one page

library(grid)
library(gridExtra)
library(gridBase)


```

> BA: I would do this a different way by re-coding and putting all the plots in one plot:

```{r onePlot}
# I would use data.table for this, not because it is the best way but because I know how to use it!
library(data.table)
mondayDT <- data.table::as.data.table(monday)
mondayDT[, ba_act := ifelse(Activity %in% c("Cooking", 
                         "Cooking (business)", 
                         "Cooking (baby)",
                         "Cooking (lunch)", 
                         "Food prep (business)", 
                         "Lunch", 
                         "Breakfast", 
                         "Dinner", 
                         "Light meal/snack"), 
                            "Cooking", # <- new code
                            NA)
         ]

mondayDT[, ba_act := ifelse(Activity %in% c("Tidy up", 
                         "Laundry", 
                         "Showering", 
                         "Showering (kids)", 
                         "Gardening", 
                         "Getting dressed", 
                         "Getting dressed (kids)",
                         "Prepare kids bag for school",
                         "Turning off applicances/Lights", 
                         "Turning on appliances/lights", 
                         "Ironing", 
                         "Feeding animals"),
                            "Tidy up", 
                            ba_act)
         ]

mondayDT[, ba_act := ifelse(Activity %in% c("Babysitting", 
                         "Charging mobile devices", 
                         "Family devotion",
                         "Exercise (Jog, walk)",
                         "Family time (chatting, games etc)",
                         "Homework (kids)",
                         "Kids bedtime",
                         "Listen to music/radio",
                         "Mobile devices (movies)",
                         "Mobile devices (games)",
                         "Mobile devices (work)",
                         "Mobile devices (browsing, social media)",
                         "Scripture study",
                         "Studying", 
                         "Reading",
                         "Watching movies (TV)"), 
                            "Leisure", 
                            ba_act)
         ]

mondayDT[, ba_act := ifelse(Activity %in% c("Farm", 
                         "Relatives", 
                         "Work", 
                         "Kava", 
                         "Church", 
                         "Church (social activities)", 
                         "Church (choir practice)", 
                         "Exercise (Jog, walk)", 
                         "Gym",
                         "Sports",
                         "School", 
                         "Going out"), 
                            "Away", 
                            ba_act)
         ]

mondayDT[, ba_act := ifelse(Activity %in% c("Driving (church)", 
                         "Driving (drop kids)", 
                         "Driving (drop relatives)",
                         "Driving (farm)", 
                         "Driving (free time)", 
                         "Driving (gym)", 
                         "Driving (home)", 
                         "Driving (Kava)", 
                         "Driving (order delivery)", 
                         "Driving (pick up kids)", 
                         "Driving (visiting relatives)", 
                         "Driving (work)", 
                         "Public transport (home)", 
                         "Public transport (work)", 
                         "Public transport (school)", 
                         "Walking (home)",  
                         "Walking (work)", 
                         "Walking (Kava)"), 
                            "Transport", 
                            ba_act)
         ]

t <- table(mondayDT$Activity, mondayDT$ba_act, useNA = "always")

kableExtra::kable(t, caption = "Test activity coding") %>%
  kable_styling()

# make a summary table for the plot
plotDT <- mondayDT[!is.na(ba_act), # excludes all NAs - see table to check coding 
                   .(count = .N), keyby = .(fixedHMS, ba_act)]

ggplot2::ggplot(plotDT, aes(x = fixedHMS, y = count, fill = ba_act)) +
  geom_col() +
  scale_fill_discrete(name="Activity (filtered)")
```

# All weekdays plotted using facets

Figure \@ref(fig:allWeekdays) shows counts for all days. We can see a few days are unknown. Also we have higher counts on Mondays.

```{r allWeekdays, fig.cap="All days"}
# use the all days table and the same coding method but across all days

allDaysDT <- data.table::as.data.table(newdata)

allDaysDT[, dayF := factor(Day,
                        levels = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday") # sets the order for the plot
                        )
       ]

allDaysDT[, ba_act := ifelse(Activity %in% c("Cooking", 
                         "Cooking (business)", 
                         "Cooking (baby)",
                         "Cooking (lunch)", 
                         "Food prep (business)", 
                         "Lunch", 
                         "Breakfast", 
                         "Dinner", 
                         "Light meal/snack"), 
                            "Cooking", # <- new code
                            NA)
         ]

allDaysDT[, ba_act := ifelse(Activity %in% c("Tidy up", 
                         "Laundry", 
                         "Showering", 
                         "Showering (kids)", 
                         "Gardening", 
                         "Getting dressed", 
                         "Getting dressed (kids)",
                         "Prepare kids bag for school",
                         "Turning off applicances/Lights", 
                         "Turning on appliances/lights", 
                         "Ironing", 
                         "Feeding animals"),
                            "Tidy up", 
                            ba_act)
         ]

allDaysDT[, ba_act := ifelse(Activity %in% c("Babysitting", 
                         "Charging mobile devices", 
                         "Family devotion",
                         "Exercise (Jog, walk)",
                         "Family time (chatting, games etc)",
                         "Homework (kids)",
                         "Kids bedtime",
                         "Listen to music/radio",
                         "Mobile devices (movies)",
                         "Mobile devices (games)",
                         "Mobile devices (work)",
                         "Mobile devices (browsing, social media)",
                         "Scripture study",
                         "Studying", 
                         "Reading",
                         "Watching movies (TV)"), 
                            "Leisure", 
                            ba_act)
         ]

allDaysDT[, ba_act := ifelse(Activity %in% c("Farm", 
                         "Relatives", 
                         "Work", 
                         "Kava", 
                         "Church", 
                         "Church (social activities)", 
                         "Church (choir practice)", 
                         "Exercise (Jog, walk)", 
                         "Gym",
                         "Sports",
                         "School", 
                         "Going out"), 
                            "Away", 
                            ba_act)
         ]

allDaysDT[, ba_act := ifelse(Activity %in% c("Driving (church)", 
                         "Driving (drop kids)", 
                         "Driving (drop relatives)",
                         "Driving (farm)", 
                         "Driving (free time)", 
                         "Driving (gym)", 
                         "Driving (home)", 
                         "Driving (Kava)", 
                         "Driving (order delivery)", 
                         "Driving (pick up kids)", 
                         "Driving (visiting relatives)", 
                         "Driving (work)", 
                         "Public transport (home)", 
                         "Public transport (work)", 
                         "Public transport (school)", 
                         "Walking (home)",  
                         "Walking (work)", 
                         "Walking (Kava)"), 
                            "Transport", 
                            ba_act)
         ]

# t <- table(allDaysDT$Activity, allDaysDT$ba_act, useNA = "always")
# 
# kableExtra::kable(t, caption = "Test activity coding (all days)") %>%
#   kable_styling()

# make a summary table for the plot
plotDT <- allDaysDT[!is.na(ba_act), # excludes all NAs - see table to check coding 
                   .(count = .N), 
                   keyby = .(fixedHMS, ba_act, dayF)] # use new day factor



ggplot2::ggplot(plotDT, aes(x = fixedHMS, y = count, fill = ba_act)) +
  geom_col() +
  facet_grid(dayF ~ .) +
  scale_fill_discrete(name="Activity (filtered)")

t <- with(allDaysDT[!is.na(ba_act)], # select the ones we re-coded only
          table(ba_act, dayF))

kableExtra::kable(t, caption = "Number of recorded coded acts by day (non recoded actas e.g. sleeping ignored)") %>%
  kable_styling()

t <- allDaysDT[, .(nRespondents = uniqueN(`Household ID`)), keyby = .(dayF)]

kableExtra::kable(t, caption = "Number of unique respondents by day (all acts)") %>%
  kable_styling()
```

There are a lot of Mondays in this data...

How many are there per village?

```{r villageDays}

dt <- allDaysDT[, .(n = uniqueN(`Household ID`)), 
                   keyby = .(Village)]



kableExtra::kable(dt, caption = "Number of respondents by village")
```

# Conclusions
